---
title: "BUAN 6357_Homework1_Peddisetty"
author: "Tharun Peddisetty"
date: "9/8/2020"
output:
  pdf_document: default
  html_document: default
---

```{r}
pacman::p_load(e1071, ggplot2, caret, rmarkdown, corrplot, knitr)
search()
theme_set(theme_classic())
options(digits = 3)
```

# 0) Data Import
```{r}
data <- read.csv("juice.csv")
```

# 1) Create data partition
```{r}
set.seed(123)
trainindex <- createDataPartition(data$Purchase, p=0.8, list= FALSE)
juice_train <- data[trainindex, ]
juice_test <- data[-trainindex, ]
```

# 2) SVM Model
### Below is the SVM model ran with Linear kernel and cost of 0.01. It is able to predict the correct classes of the drinks with 83.5% accuracy.
```{r}

svm1 <- svm(Purchase~., data=juice_train,kernel= "linear", cost=0.01)
summary(svm1)


 ## Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# accuracy
(sum(diag(conf.matrix))) / sum(conf.matrix)
```

# 3) Training and test error rates
### Error rate is given by total incorrect classifications divided by total observations. Typically calculated as (1-accuracy)

### For Cost: 0.01
#### * Training Error rate = 17%
#### * Test Error rate = 16.5%
```{r}
 ## Train Performance Evaluation ##
pred1 <- predict(svm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train Error
1-(sum(diag(conf.matrix))) / sum(conf.matrix)

 ## Test Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
1-(sum(diag(conf.matrix))) / sum(conf.matrix)
```


# 4) Using tune() function to select optimal cost
### Cost with least error is 0.51 from the  below code with accuracy of 82.5%
```{r}
set.seed(123)
tunesvm1 <- tune(svm, Purchase~., data = juice_train, kernel='linear',
     ranges = list(cost = seq(0.01,10,by=0.5)))

summary(tunesvm1)
plot(tunesvm1)


  ## Best SVM Model ##
bestsvm1 <- tunesvm1$best.model
summary(bestsvm1)


bestpred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix2 <- table(Predicted = bestpred1, Actual = juice_test$Purchase)
conf.matrix2

  # accuracy
(sum(diag(conf.matrix2))) / sum(conf.matrix2)
```

# 5) Train and Test errors using best Cost = 3.01

#### * Training Error rate:  16.625
#### * Test Error rate: 17.5

```{r}
## Train Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train error
print(paste("Training Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))

 ## Test Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
print(paste("Test Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))
```

# 6) SVM using radial kernel
### The radial kernel SVM model with cost 0.01 has a predictive accuracy of 61%

#### * Best Model at Cost = 0.51
#### * Accuracy = 85%

#### * Training Error rate: 15.375%
#### * Test Error rate: 15%
```{r}
svm1 <- svm(Purchase~., data=juice_train,kernel= "radial",cost=0.01)
summary(svm1)


 ## Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# accuracy
(sum(diag(conf.matrix))) / sum(conf.matrix)



 ## Train Performance Evaluation ##
pred1 <- predict(svm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train Error
print(paste("Training Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))

 ## Test Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
print(paste("Test Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))


#TUNING
set.seed(123)
tunesvm1 <- tune(svm, Purchase~., data = juice_train, kernel='radial',
     ranges = list(cost = seq(0.01,10,by=0.5)))

summary(tunesvm1)
plot(tunesvm1)


  ## Best SVM Model ##
bestsvm1 <- tunesvm1$best.model
summary(bestsvm1)


bestpred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix2 <- table(Predicted = bestpred1, Actual = juice_test$Purchase)
conf.matrix2

  # accuracy
print(paste("Accuracy: ",(sum(diag(conf.matrix2))) / sum(conf.matrix2)))



 ## Train Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train error
print(paste("Training Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))

 ## Test Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
print(paste("Test Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))
```
# 7) SVM using polynomial kernel with degree=2
### The polynomial kernel SVM model with cost 0.01 has a predictive accuracy of 61%

#### * Best Model at Cost = 8.51
#### * Accuracy = 83%

#### * Training Error rate: 16.25%
#### * Test Error rate: 17%
```{r}
svm1 <- svm(Purchase~., data=juice_train,kernel= "polynomial",degree=2,cost=0.01)
summary(svm1)


 ## Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# accuracy
(sum(diag(conf.matrix))) / sum(conf.matrix)



 ## Train Performance Evaluation ##
pred1 <- predict(svm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train Error
1-(sum(diag(conf.matrix))) / sum(conf.matrix)

 ## Test Performance Evaluation ##
pred1 <- predict(svm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
1-(sum(diag(conf.matrix))) / sum(conf.matrix)


#TUNING
set.seed(123)
tunesvm1 <- tune(svm, Purchase~., data = juice_train, kernel= "polynomial",degree=2,
     ranges = list(cost = seq(0.01,10,by=0.5)))

summary(tunesvm1)
plot(tunesvm1)


  ## Best SVM Model ##
bestsvm1 <- tunesvm1$best.model
summary(bestsvm1)


bestpred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix2 <- table(Predicted = bestpred1, Actual = juice_test$Purchase)
conf.matrix2

  # accuracy
print(paste("Accuracy: ",(sum(diag(conf.matrix2))) / sum(conf.matrix2)))


 ## Train Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_train)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_train$Purchase)
conf.matrix
  
# Train error
print(paste("Training Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))

 ## Test Performance Evaluation ##
pred1 <- predict(bestsvm1, juice_test)

# confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = juice_test$Purchase)
conf.matrix
  
# Test Error
print(paste("Test Error rate: ",1-(sum(diag(conf.matrix))) / sum(conf.matrix)))
```

# 8) Best Model

### SVM with radial kernel gives us the best results.

### It has the highest accuracy of 85% when deployed on the test data.

### It also has the least training and test error rate of about 15% each which is almost 1% lesser than other respective error rates.

